---
title: Spatial analysis of the association between LLIN use and malaria prevalence in a longitudinal cohort in northeast Uganda
subtitle: 
titlerunning: LLIN use and malaria prevalence in Uganda
authorrunning: 
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

authors: 
- name: Chong Kim
  address: Department of Biostatistics and Informatics, University of Colorado Denver, Aurora, CO, USA
  email: chong.kim@ucdenver.edu
- name: Dorothy Echodu
  address: Pilgrim Africa
  email: djf@wef
- name: Humphrey Wanzira
  address: Pilgrim Africa
  email: djf@wef
- name: Yeka Adoke
  address: Pilgrim Africa
  email: djf@wef
- name: Kathryn L. Colborn
  address: Department of Biostatistics and Informatics, University of Colorado Denver, Aurora, CO, USA
  email: Kathryn.colborn@ucdenver.edu


keywords:
- LLIN
- Spatial analysis
- Malaria
- RDT
- Microscopy

#PACS: 
#- PAC1
#- superPAC
    
MSC:
#- MSC code 1
#- MSC code 2    

abstract: |
  The text of your abstract.  150 -- 250 words.

bibliography: bibliography.bib
output: 
    pdf_document:
    #rticles::springer_article
        #latex_engine: xelatex
        template: template.tex
header-includes:
   - \usepackage[margin=1in]{geometry}
   - \usepackage{multirow}
   - \usepackage{multicol}
   - \usepackage{xcolor}
   - \usepackage{textcomp}
   - \usepackage{colortbl}
   - \usepackage{longtable}
   - \usepackage[T1]{fontenc}
   - \usepackage{lmodern}
   - \usepackage{booktabs,tabularx,ragged2e,dcolumn,caption} 
   - \usepackage{graphicx}
   - \usepackage{float}
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(captioner)

## Global options
#options(max.print="75")
opts_chunk$set(echo=FALSE,
				 #cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               #eval.after = 'fig.cap',
               fig.pos = "H"
               )
#opts_knit$set(width=75)
opts_knit$set(root.dir = normalizePath("~/Documents/Projects/DrColborn/UgandaNets"))

```

# Introduction {#intro}

Your text comes here. Separate text sections with

# Methods {#sec:methods}

Text with citations by @Galyardt14mmm, [@Mislevy06Cog].

## Subsection title {#sec:methodssub1}

as required. Don't forget to give each section
and subsection a unique label (see Sect. \ref{sec:methods}).

#### Paragraph headings 

Use paragraph headings as needed.

\begin{align}
a^2+b^2=c^2
\end{align}


# Results {#sec:results}

```{r tablenumbering}
# captioning
table_nums <- captioner::captioner(prefix = "Table ")
tab.1_cap <- table_nums(name = "tab_1",
                        caption = "Demographic characteristics, net usage, and malaria status of study population.")

tab.2_cap <- table_nums(name = "tab_2",
                        caption = "Coefficients from spatial model")
# referecing function
f.ref <- function(x) {
  stringr::str_extract(table_nums(x), "[^:]*")
}

# from https://datascienceplus.com/r-markdown-how-to-number-and-reference-tables/
```

Something something about table 1.

`r table_nums('tab_1')`

```{r tab1, results='asis', fig.cap = tab.1_cap}
options(ztable.type="latex")
options(ztable.zebra=NULL)
#options(ztable.colnames.bold=TRUE)
library(dplyr)
library(knitr)
library(moonBook)
library(kableExtra)
library(ztable)
library(xtable)
library(tables)
tab1 <- readRDS("./data/process/table1.RDS")
mytable(stime ~ 
        age +
        num_hh +
        num_net +
        netCov +
        Netptwo +
        rdtPos_tested +
        rdtRate +
        micPos_tested +
        micRate
    , data=tab1) %>%
addComma %>%
ztable %>%
addrgroup(rgroup=c("Demographic","Net usage","Malaria"),
          n.rgroup=c(2, 5, 4), cspan.rgroup=1) %>%
#addSigColor(level=0.1,bg="yellow",color="red") %>%
update_ztable(., size=4 
              #,align=c("l","c","c","c","c","r")
              ) %>%
print(type='latex', caption.placement = "top")
```



`r table_nums('tab_2')`

```{r tab2, results='asis', fig.cap = tab.2_cap}
#options(ztable.type="latex")
options(ztable.zebra=NULL)
#options("scipen"=999, digits=3)
library(Hmisc)
library(geoR)
library(geoRglm)
library(coda)
library(knitr)
pkb <- readRDS("./data/results/pkb.RDS")
pkb.mcmc.tune <- mcmc.control(S.scale = 0.005, thin = 1)
pkb_all <- readRDS("./data/results/pkb_allvars.RDS")
# - - - - - - - - - - - - - - - #
# NetCov w/ Surface Trend
# - - - - - - - - - - - - - - - #

# create dataframe containing HPD and median for betas
rt <- sapply(1:nrow(pkb$posterior$beta$sample), function(x) {
  c(HPDinterval(create.mcmc.coda(pkb$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune), prob = 0.95), median(create.mcmc.coda(pkb$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune)))
})

# merge HPD of sigma^2 and phi
rt <- cbind(rt, c(HPDinterval(create.mcmc.coda(pkb$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune))))
rt <- cbind(rt, c(HPDinterval(create.mcmc.coda(pkb$posterior$phi$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb$posteriore$phi$sample ,mcmc.input = pkb.mcmc.tune))))
# merge the means as row and exponentiate
rt <- exp(rbind(rt, c(pkb$posterior$beta$mean, pkb$posterior$sigmasq$mean, pkb$posterior$phi$mean)))
rownames(rt) <- c("95% LCI","95% UCI","Median","Mean")
colnames(rt) <- c("intercep","netCov","stime2","stime3","stime4","longitude","latitude", "sig^2","phi")


# - - - - - - - - - - - - - - - #
# RDT: Netptwo w/ Surface Trend
# - - - - - - - - - - - - - - - #

rt4 <- sapply(1:nrow(pkb_all[[3]][[2]]$posterior$beta$sample), function(x) {
  c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[2]]$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune), prob = 0.95), median(create.mcmc.coda(pkb_all[[3]][[2]]$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune)))
})

# merge HPD of sigma^2 and phi
rt4 <- cbind(rt4, c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[2]]$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb_all[[3]][[2]]$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune))))
rt4 <- cbind(rt4, c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[2]]$posterior$phi$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb_all[[3]][[2]]$posteriore$phi$sample ,mcmc.input = pkb.mcmc.tune))))
# merge the means as row and exponentiate
rt4 <- exp(rbind(rt4, c(pkb_all[[3]][[2]]$posterior$beta$mean, pkb_all[[3]][[2]]$posterior$sigmasq$mean, pkb_all[[3]][[2]]$posterior$phi$mean)))
rownames(rt4) <- c("95% LCI","95% UCI","Median","Mean")
colnames(rt4) <- c("intercep","netCov","stime2","stime3",'stime4',"longitude","latitude", "sig^2","phi")



# - - - - - - - - - - - - - - - #
# MIC: netcov w/ Surface Trend
# - - - - - - - - - - - - - - - #

pkb<- readRDS("~/Documents/Projects/DrColborn/UgandaNets/data/results/pkbm.RDS")

# create dataframe containing HPD and median for betas
rt6 <- sapply(1:nrow(pkb$posterior$beta$sample), function(x) {
  c(HPDinterval(create.mcmc.coda(pkb$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune), prob = 0.95), median(create.mcmc.coda(pkb$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune)))
})

# merge HPD of sigma^2 and phi
rt6 <- cbind(rt6, c(HPDinterval(create.mcmc.coda(pkb$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune))))
rt6 <- cbind(rt6, c(HPDinterval(create.mcmc.coda(pkb$posterior$phi$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb$posteriore$phi$sample ,mcmc.input = pkb.mcmc.tune))))
# merge the means as row and exponentiate
rt6 <- exp(rbind(rt6, c(pkb$posterior$beta$mean, pkb$posterior$sigmasq$mean, pkb$posterior$phi$mean)))
rownames(rt6) <- c("95% LCI","95% UCI","Median","Mean")
colnames(rt6) <- c("intercep","netCov","stime2","stime3","stime4","longitude","latitude", "sig^2","phi")



# - - - - - - - - - - - - - - - #
# MIC: netptwo w/ Surface Trend
# - - - - - - - - - - - - - - - #

rt10 <- sapply(1:nrow(pkb_all[[3]][[4]]$posterior$beta$sample), function(x) {
  c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[4]]$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune), prob = 0.95), median(create.mcmc.coda(pkb_all[[3]][[4]]$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune)))
})

# merge HPD of sigma^2 and phi
rt10 <- cbind(rt10, c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[4]]$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb_all[[3]][[4]]$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune))))
rt10 <- cbind(rt10, c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[4]]$posterior$phi$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb_all[[3]][[4]]$posteriore$phi$sample ,mcmc.input = pkb.mcmc.tune))))
# merge the means as row and exponentiate
rt10 <- exp(rbind(rt10, c(pkb_all[[3]][[4]]$posterior$beta$mean, pkb_all[[3]][[4]]$posterior$sigmasq$mean, pkb_all[[3]][[4]]$posterior$phi$mean)))
rownames(rt10) <- c("95% LCI","95% UCI","Median","Mean")
colnames(rt10) <- c("intercep","netCov","stime2","stime3",'stime4',"longitude","latitude", "sig^2","phi")

#tab2 <- data.frame(
                   #rdt_nc1=round(as.data.frame(t(rt[,-1]))[,3], 3),
                   #rdt_nc2=round(as.data.frame(t(rt[,-1]))[,1], 3),
                   #rdt_nc3=round(as.data.frame(t(rt[,-1]))[,2], 3),
                   
                   #rdt_npt1=round(as.data.frame(t(rt4[,-1]))[,3], 3),
                   #rdt_npt2=round(as.data.frame(t(rt4[,-1]))[,1], 3),
                   #rdt_npt3=round(as.data.frame(t(rt4[,-1]))[,2], 3),
                   
                   #mic_nc1=round(as.data.frame(t(rt6[,-1]))[,3], 3),
                   #mic_nc2=round(as.data.frame(t(rt6[,-1]))[,1], 3),
                   #mic_nc3=round(as.data.frame(t(rt6[,-1]))[,2], 3),
                   
                   #mic_npt1=round(as.data.frame(t(rt10[,-1]))[,3], 3),
                   #mic_npt2=round(as.data.frame(t(rt10[,-1]))[,1], 3),
                   #mic_npt3=round(as.data.frame(t(rt10[,-1]))[,2], 3)
                   #)

tab2 <- data.frame(
                   rdt_nc=paste0(formatC(as.data.frame(t(rt)[-1,])[,3], digits=3, format="fg", flag="#"),
                              " (",
                              formatC(as.data.frame(t(rt)[-1,])[,1], digits=3, format="fg", flag="#"),
                              ", ",
                              formatC(as.data.frame(t(rt)[-1,])[,2], digits=3, format="fg", flag="#"),
                              ")"), 
                   rdt_npt=paste0(formatC(as.data.frame(t(rt4)[-1,])[,3], digits=3, format="fg"),
                              " (",
                              formatC(as.data.frame(t(rt4)[-1,])[,1], digits=3, format="fg"),
                              ", ",
                              formatC(as.data.frame(t(rt4)[-1,])[,2], digits=3, format="fg"),
                              ")"), 
                   mic_nc=paste0(formatC(as.data.frame(t(rt6)[-1,])[,3], digits=3, format="fg"),
                              " (",
                              formatC(as.data.frame(t(rt6)[-1,])[,1], digits=3, format="fg"),
                              ", ",
                              formatC(as.data.frame(t(rt6)[-1,])[,2], digits=3, format="fg"),
                              ")"), 
                   mic_npt=paste0(formatC(as.data.frame(t(rt10)[-1,])[,3], digits=3, format="fg"),
                              " (",
                              formatC(as.data.frame(t(rt10)[-1,])[,1], digits=3, format="fg"),
                              ", ",
                              formatC(as.data.frame(t(rt10)[-1,])[,2], digits=3, format="fg"),
                              ")")
                   )

rownames(tab2) <- rownames(t(rt))[-1]
Hmisc::label(tab2[["rdt_nc"]]) <- "Net Coverage"
Hmisc::label(tab2[["rdt_npt"]]) <- ">= 1 net per 2"
Hmisc::label(tab2[["mic_nc"]]) <- "Net Coverage"
Hmisc::label(tab2[["mic_npt"]]) <- ">= 1 net per 2"

colnames(tab2) <- c("Net Cov",">= 1 net per 2","Net Cov",">= 1 net per 2")

#print(xtable(tab2,
             #align=paste(rep("r", ncol(tab2) + 1), collapse = "")
             #))
#ztable(tab2,
       #zebra.type = 1,
       #align=paste(rep("r", ncol(tab2) + 1), collapse = "")
       #)  %>%
#print(type = "latex")
kable(tab2, align = c("c"),
      digits = 3,
      booktabs = TRUE) %>%
    kable_styling("pandoc" ,
                  # c("striped","bordered"), 
                  full_width = F,
                  font_size = 7) %>%
    add_header_above(c(" ", "RDT+" = 2, "MIC+" = 2)) %>%
    add_header_above(c(" ", "Dependent Variable" = 4)) %>%
    group_rows("Time", 2, 4) %>%
    group_rows("Spatial", 5, 8) 
```




```{r agg_rdt+, include=FALSE}
library(sp)
library(rgdal)
library(dplyr)

rm(list=ls())
### df <- readRDS("ug_ct2_final.RDS") # This is the original data with the CleanS1S2....csv file
df <- readRDS("./data/process/final_hh_df.RDS")

### A. Convert data into SpatialPointsDataFrame
spdf <- SpatialPointsDataFrame(coords = df[,c("longitude","latitude")], data = subset(df, select = 1:ncol(df)), proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))

### B. Import the SpatialPolygonDataFrame based on the downloaded SHP file
# First subset the two districts that hae received the intervention

uganda_shp <- readOGR(dsn = "/home/ck1/Documents/Projects/DrColborn/UgandaNets/data/UGA_adm_shp", layer = "UGA_adm4")

### Here is another shp file from the people at IDS 

uganda_shpa <- readOGR(dsn = "/home/ck1/Documents/Projects/DrColborn/UgandaNets/data/PIL_shp", layer = "pilgrim_villages")

subset <- uganda_shpa[uganda_shpa$subcounty == 2,] # we want subcounty 2


temp <- over(spdf, subset) # here we're getting those observations from the spdf points dataframe that intersects with the subset polygon dataframe
temp <- cbind(as.data.frame(df), temp[3]) # merge in the village column
poly1 <- subset # create new subset so that we can join 
poly1@data <- left_join(poly1@data, aggregate(rdtRate ~ village, FUN = mean, data = temp)) # here we are aggregating across all survey time points
poly1@data <- left_join(poly1@data, aggregate(netCov ~ village, FUN = mean, data = temp)) # same thing for the net coverage

#### Plot RDT+, MIC+, by survey times...
md_time <- temp %>%
  mutate(mi = ifelse(is.na(num_hh) == TRUE, 1, 0)) %>%
  select(village, stime, mi,micRate, rdtRate, netCov, Netptwo, oneNet, slept_net_p) %>%
  group_by(village, stime) %>%
  summarize_all(funs(mean(., na.rm=TRUE))) %>%
  filter(is.na(village) == FALSE)

poly2 <- poly1
poly2 <- broom::tidy(poly2)
poly2$village <- as.numeric(poly2$id) - 54
poly2 <- left_join(poly2, md_time)

library(ggmap)
library(gridExtra)
library(lattice)
#map <- get_map(location = c(lon = 34.1, lat = 1.75), zoom = 12, maptype = "hybrid")
map <- readRDS("/home/ck1/Documents/Projects/DrColborn/UgandaNets/data/process/map.RDS") # in the process folder
# function to extract legend only
g_legend <- function(a.gplot){ tmp <- ggplot_gtable(ggplot_build(a.gplot)) 
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box") 
    legend <- tmp$grobs[[leg]] 
    return(legend)} 

library(tidyr)
f1df <- gather(poly2, vars, rates, micRate, rdtRate)
f1df <- data.frame(f1df) %>%
    mutate(vars = ifelse(vars == 'rdtRate', 'RDT', 'Microscopy')) 
f1df$vars <- factor(f1df$vars, levels = c('RDT','Microscopy'))

```

```{r googmap_overlay, fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="Maps of microscopy and rapid diagnostic test positivity using village shapes by survey time."}
library(RColorBrewer)
f.ref <- function(x) {
  stringr::str_extract(table_nums(x), "[^:]*")
}
ggmap(map) +
    geom_polygon(aes(fill = rates, x = long, y = lat, group = group),
                 data = f1df[f1df$stime %in% c(1,2,3,4),] %>%
                     mutate(stime = ifelse(stime == 1, "Survey 1", ifelse(stime == 2, "Survey 2", ifelse(stime == 3, "Survey 3", "Survey 4")))),
                 alpha = 0.95,
                 color = "black",
                 size = 0.2) +
theme(axis.text.x = element_text(size=7, angle=45, hjust = 1)) +
facet_grid(vars ~ stime) +
#scale_fill_gradient2(low = "yellow", mid = "orange", high = "red", # colors
                     #breaks = quantile(0:1),
                     #limits = c(0,1),
                     #midpoint = 0.5, name = paste0("rate")
                     #)
scale_fill_gradientn(
                     colours=brewer.pal(10,"YlOrRd"),
                     #colours=rev(brewer.pal(10,"Spectral")),
                     breaks = quantile(0:1),
                     limits = c(0,1),
                     #midpoint = 0.5, 
                     name = paste0("rate")
                     )
#ggsave("fig1.png")
```




```{r fig2, fig.align='center', fig.width=6.1, fig.height=9.5, fig.cap=paste0("Relationship between LLIN use and Positivity.", "\\textbf{A}" ,": Net coverage (i.e. proportion of net/tested in HH) vs. positivity. ", " \\textbf{B} " ," : Sleeping under the net (i.e. Proportion of people sleeping under/per net in HH) and positivity. ", " \\textbf{C} ", " : Net per two (i.e.", ">","50","\\%"," people in HH) and positivity")}
library(ggplot2)
library(gridExtra)
library(gtable)
library(grid)
#-- make df that will allow facet_* by 
spline_k <- 4
f2df <- df %>%
    filter(county == 2) %>%
    gather(., vars, rates, micRate, rdtRate) %>%
    mutate(vars = ifelse(vars == "rdtRate", "RDT", "Microscopy"),
           Netptwo = ifelse(Netptwo == 1, ">50%", "<50%"))
f2a <- ggplot(f2df, aes(x = netCov, y = rates, color = as.factor(stime))) + 
  #geom_smooth(method = 'gam', formula = y ~ s(x, bs="cs", k=spline_k)) + 
  geom_smooth(method = 'lm') + 
  facet_grid(. ~ vars)+
  theme_light() + 
  ggtitle("A") +
  labs(color = "Survey Time") + 
  scale_color_manual(values=c("#000000", "#f20505","#f9d70b", '#f4a460')) + 
  theme(legend.position="bottom", axis.title.y = element_blank(), 
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.title.x = element_blank()
        ) +
  coord_cartesian(ylim = c(0, 0.6), xlim=c(0,1))

f2c <- ggplot(f2df, aes(x = as.factor(Netptwo), y = rates, fill = as.factor(stime))) + 
  geom_boxplot() +
  #facet_grid(vars ~ .)+
  facet_grid(. ~ vars)+
  labs(fill = "Survey Time") +
  scale_fill_manual(values=c("#000000", "#f20505","#f9d70b", '#f4a460')) + 
  ggtitle("C") +
  theme_light() + 
  theme(legend.position="bottom", axis.title.y = element_blank(), axis.title.x = element_blank()) 

f2b <- ggplot(f2df, aes(x = slept_net_p, y = rates, color = as.factor(stime))) + 
  #geom_smooth(method = 'gam', formula = y ~ s(x, bs="cs", k=spline_k)) + 
  geom_smooth(method = 'lm') + 
  facet_grid(. ~ vars)+
  theme_light() + 
  labs(color = "Survey Time") + 
  ggtitle("B") +
  scale_color_manual(values=c("#000000", "#f20505","#f9d70b", '#f4a460')) + 
  theme(legend.position="bottom", axis.title.y = element_blank(), 
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.title.x = element_blank()) +
  coord_cartesian(ylim = c(0, 0.6), xlim=c(0,1))

mylegend<-g_legend(f2a)
f2 <- grid.arrange(
  arrangeGrob(f2a + theme(legend.position="none"),
              f2b + theme(legend.position="none"),
              f2c + theme(legend.position="none")
              ,nrow=3,
              left = textGrob("Rate", rot = 90, vjust = 1),
              bottom = textGrob("Coverate Rate")
              ),
  mylegend, nrow=2,heights=c(12, 1) 
  )
#library(cowplot)
#plot_grid(f2a, f2b, f2c, 
          #ncol=1,
          #axis='1',
          #labels = "AUTO",
          #align = 'v'
          #)
#ggsave(file="./fig2.png", f2)
table_nums <- captioner::captioner(prefix = "Table ")
```


## Subsection title {#sec:2}

Referencing `r f.ref('tab_1')` is cool. as required. Don't forget to give each section
and subsection a unique label (see Sect. \ref{sec:results}).

#### Paragraph headings 

Use paragraph headings as needed.

\begin{align}
a^2+b^2=c^2
\end{align}






# References
