---
title: Spatial analysis of the association between LLIN use and malaria prevalence in a longitudinal cohort in northeast Uganda
subtitle: 
titlerunning: LLIN use and malaria prevalence in Uganda
authorrunning: 
thanks: | 
    Grants or other notes about the article that should go on the front 
    page should be placed here. General acknowledgments should be placed at the
    end of the article.

authors: 
- name: Chong Kim
  address: Department of Biostatistics and Informatics, University of Colorado Denver, Aurora, CO, USA
  email: chong.kim@ucdenver.edu
- name: Dorothy Echodu
  address: Pilgrim Africa
  email: djf@wef
- name: Humphrey Wanzira
  address: Pilgrim Africa
  email: djf@wef
- name: Yeka Adoke
  address: Pilgrim Africa
  email: djf@wef
- name: Kathryn L. Colborn
  address: Department of Biostatistics and Informatics, University of Colorado Denver, Aurora, CO, USA
  email: Kathryn.colborn@ucdenver.edu


keywords:
- LLIN
- Spatial analysis
- Malaria
- RDT
- Microscopy

#PACS: 
#- PAC1
#- superPAC
    
MSC:
#- MSC code 1
#- MSC code 2    

abstract: |
  The text of your abstract.  150 -- 250 words.

bibliography: bibliography.bib
output: 
    rticles::springer_article
        #latex_engine: xelatex
header-includes:
   - \usepackage[margin=1in]{geometry}
   - \usepackage{multirow}
   - \usepackage{multicol}
   - \usepackage{xcolor}
   - \usepackage{textcomp}
   - \usepackage{colortbl}
   - \usepackage{longtable}
   - \usepackage[T1]{fontenc}
   - \usepackage{lmodern}
   - \usepackage{booktabs,tabularx,ragged2e,dcolumn,caption} 
   - \usepackage{graphicx}
   - \usepackage{float}
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)

## Global options
#options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
#opts_knit$set(width=75)
opts_knit$set(root.dir = normalizePath("~/Documents/Projects/DrColborn/UgandaNets"))

# captioning
table_nums <- captioner::captioner(prefix = "Table ")
tab.1_cap <- table_nums(name = "tab_1",
                        caption = "Demographic characteristics, net usage, and malaria status of study population.")

tab.2_cap <- table_nums(name = "tab_2",
                        caption = "Coefficients from spatial model")
# referecing function
f.ref <- function(x) {
  stringr::str_extract(table_nums(x), "[^:]*")
}

# from https://datascienceplus.com/r-markdown-how-to-number-and-reference-tables/
```

# Introduction {#intro}

Your text comes here. Separate text sections with

# Methods {#sec:methods}

Text with citations by @Galyardt14mmm, [@Mislevy06Cog].

## Subsection title {#sec:methodssub1}

as required. Don't forget to give each section
and subsection a unique label (see Sect. \ref{sec:methods}).

#### Paragraph headings 

Use paragraph headings as needed.

\begin{align}
a^2+b^2=c^2
\end{align}


# Results {#sec:results}

`r table_nums('tab_1')`

```{r tab1, results='asis', fig.cap = tab.1_cap}
options(ztable.type="latex")
options(ztable.zebra=NULL)
library(dplyr)
library(knitr)
library(moonBook)
library(kableExtra)
library(ztable)
library(xtable)
library(tables)
tab1 <- readRDS("./data/process/table1.RDS")
mytable(stime ~ age +
        #gender +
        num_hh +
        num_net +
        netCov +
        Netptwo +
        hh_tested +
        rdtRate +
        micRate
    , data=tab1) %>%
addComma %>%
ztable %>%
addrgroup(rgroup=c("Demographic","Net usage","Malaria"),
          n.rgroup=c(2, 5, 3), cspan.rgroup=1) %>%
addSigColor(level=0.1,bg="yellow",color="red") %>%
update_ztable(., size=4 
              #,align=c("l","c","c","c","c","r")
              ) %>%
print(type='latex')
```

`r table_nums('tab_2')`

```{r tab2, results='asis', fig.cap = tab.2_cap}
#options(ztable.type="latex")
#options(ztable.zebra=NULL)
options("scipen"=999, digits=3)
library(Hmisc)
library(geoR)
library(geoRglm)
library(coda)
library(knitr)
pkb <- readRDS("./data/results/pkb.RDS")
pkb.mcmc.tune <- mcmc.control(S.scale = 0.005, thin = 1)
pkb_all <- readRDS("./data/results/pkb_allvars.RDS")

# - - - - - - - - - - - - - - - #
# NetCov w/ Surface Trend
# - - - - - - - - - - - - - - - #

# create dataframe containing HPD and median for betas
rt <- sapply(1:nrow(pkb$posterior$beta$sample), function(x) {
  c(HPDinterval(create.mcmc.coda(pkb$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune), prob = 0.95), median(create.mcmc.coda(pkb$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune)))
})

# merge HPD of sigma^2 and phi
rt <- cbind(rt, c(HPDinterval(create.mcmc.coda(pkb$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune))))
rt <- cbind(rt, c(HPDinterval(create.mcmc.coda(pkb$posterior$phi$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb$posteriore$phi$sample ,mcmc.input = pkb.mcmc.tune))))
# merge the means as row and exponentiate
rt <- exp(rbind(rt, c(pkb$posterior$beta$mean, pkb$posterior$sigmasq$mean, pkb$posterior$phi$mean)))
rownames(rt) <- c("95% LCI","95% UCI","Median","Mean")
colnames(rt) <- c("intercep","netCov","stime2","stime3","stime4","longitude","latitude", "sig^2","phi")


# - - - - - - - - - - - - - - - #
# RDT: Netptwo w/ Surface Trend
# - - - - - - - - - - - - - - - #

rt4 <- sapply(1:nrow(pkb_all[[3]][[2]]$posterior$beta$sample), function(x) {
  c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[2]]$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune), prob = 0.95), median(create.mcmc.coda(pkb_all[[3]][[2]]$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune)))
})

# merge HPD of sigma^2 and phi
rt4 <- cbind(rt4, c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[2]]$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb_all[[3]][[2]]$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune))))
rt4 <- cbind(rt4, c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[2]]$posterior$phi$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb_all[[3]][[2]]$posteriore$phi$sample ,mcmc.input = pkb.mcmc.tune))))
# merge the means as row and exponentiate
rt4 <- exp(rbind(rt4, c(pkb_all[[3]][[2]]$posterior$beta$mean, pkb_all[[3]][[2]]$posterior$sigmasq$mean, pkb_all[[3]][[2]]$posterior$phi$mean)))
rownames(rt4) <- c("95% LCI","95% UCI","Median","Mean")
colnames(rt4) <- c("intercep","netCov","stime2","stime3",'stime4',"longitude","latitude", "sig^2","phi")


rt6 <- sapply(1:nrow(pkb_all[[1]][[4]]$posterior$beta$sample), function(x) {
  c(HPDinterval(create.mcmc.coda(pkb_all[[1]][[4]]$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune), prob = 0.95), median(create.mcmc.coda(pkb_all[[1]][[4]]$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune)))
})

# - - - - - - - - - - - - - - - #
# MIC: netcov w/ Surface Trend
# - - - - - - - - - - - - - - - #

# merge HPD of sigma^2 and phi
rt6 <- cbind(rt6, c(HPDinterval(create.mcmc.coda(pkb_all[[1]][[4]]$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb_all[[1]][[4]]$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune))))
rt6 <- cbind(rt6, c(HPDinterval(create.mcmc.coda(pkb_all[[1]][[4]]$posterior$phi$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb_all[[1]][[4]]$posteriore$phi$sample ,mcmc.input = pkb.mcmc.tune))))
# merge the means as row and exponentiate
rt6 <- exp(rbind(rt6, c(pkb_all[[1]][[4]]$posterior$beta$mean, pkb_all[[1]][[4]]$posterior$sigmasq$mean, pkb_all[[1]][[4]]$posterior$phi$mean)))
rownames(rt6) <- c("95% LCI","95% UCI","Median","Mean")
colnames(rt6) <- c("intercep","netCov","stime2","stime3",'stime4',"longitude","latitude", "sig^2","phi")



# - - - - - - - - - - - - - - - #
# MIC: netptwo w/ Surface Trend
# - - - - - - - - - - - - - - - #

rt10 <- sapply(1:nrow(pkb_all[[3]][[4]]$posterior$beta$sample), function(x) {
  c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[4]]$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune), prob = 0.95), median(create.mcmc.coda(pkb_all[[3]][[4]]$posterior$beta$sample[x,],mcmc.input = pkb.mcmc.tune)))
})

# merge HPD of sigma^2 and phi
rt10 <- cbind(rt10, c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[4]]$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb_all[[3]][[4]]$posterior$sigmasq$sample ,mcmc.input = pkb.mcmc.tune))))
rt10 <- cbind(rt10, c(HPDinterval(create.mcmc.coda(pkb_all[[3]][[4]]$posterior$phi$sample ,mcmc.input = pkb.mcmc.tune)), median(create.mcmc.coda(pkb_all[[3]][[4]]$posteriore$phi$sample ,mcmc.input = pkb.mcmc.tune))))
# merge the means as row and exponentiate
rt10 <- exp(rbind(rt10, c(pkb_all[[3]][[4]]$posterior$beta$mean, pkb_all[[3]][[4]]$posterior$sigmasq$mean, pkb_all[[3]][[4]]$posterior$phi$mean)))
rownames(rt10) <- c("95% LCI","95% UCI","Median","Mean")
colnames(rt10) <- c("intercep","netCov","stime2","stime3",'stime4',"longitude","latitude", "sig^2","phi")

#tab2 <- data.frame(
                   #rdt_nc1=round(as.data.frame(t(rt[,-1]))[,3], 3),
                   #rdt_nc2=round(as.data.frame(t(rt[,-1]))[,1], 3),
                   #rdt_nc3=round(as.data.frame(t(rt[,-1]))[,2], 3),
                   
                   #rdt_npt1=round(as.data.frame(t(rt4[,-1]))[,3], 3),
                   #rdt_npt2=round(as.data.frame(t(rt4[,-1]))[,1], 3),
                   #rdt_npt3=round(as.data.frame(t(rt4[,-1]))[,2], 3),
                   
                   #mic_nc1=round(as.data.frame(t(rt6[,-1]))[,3], 3),
                   #mic_nc2=round(as.data.frame(t(rt6[,-1]))[,1], 3),
                   #mic_nc3=round(as.data.frame(t(rt6[,-1]))[,2], 3),
                   
                   #mic_npt1=round(as.data.frame(t(rt10[,-1]))[,3], 3),
                   #mic_npt2=round(as.data.frame(t(rt10[,-1]))[,1], 3),
                   #mic_npt3=round(as.data.frame(t(rt10[,-1]))[,2], 3)
                   #)

tab2 <- data.frame(
                   rdt_nc=paste0(formatC(as.data.frame(t(rt)[-1,])[,3], digits=3, format="fg", flag="#"),
                              " (",
                              formatC(as.data.frame(t(rt)[-1,])[,1], digits=3, format="fg", flag="#"),
                              ", ",
                              formatC(as.data.frame(t(rt)[-1,])[,2], digits=3, format="fg", flag="#"),
                              ")"), 
                   rdt_npt=paste0(formatC(as.data.frame(t(rt4)[-1,])[,3], digits=3, format="fg"),
                              " (",
                              formatC(as.data.frame(t(rt4)[-1,])[,1], digits=3, format="fg"),
                              ", ",
                              formatC(as.data.frame(t(rt4)[-1,])[,2], digits=3, format="fg"),
                              ")"), 
                   mic_nc=paste0(formatC(as.data.frame(t(rt6)[-1,])[,3], digits=3, format="fg"),
                              " (",
                              formatC(as.data.frame(t(rt6)[-1,])[,1], digits=3, format="fg"),
                              ", ",
                              formatC(as.data.frame(t(rt6)[-1,])[,2], digits=3, format="fg"),
                              ")"), 
                   mic_npt=paste0(formatC(as.data.frame(t(rt10)[-1,])[,3], digits=3, format="fg"),
                              " (",
                              formatC(as.data.frame(t(rt10)[-1,])[,1], digits=3, format="fg"),
                              ", ",
                              formatC(as.data.frame(t(rt10)[-1,])[,2], digits=3, format="fg"),
                              ")")
                   )

rownames(tab2) <- rownames(t(rt))[-1]
Hmisc::label(tab2[["rdt_nc"]]) <- "Net Coverage"
Hmisc::label(tab2[["rdt_npt"]]) <- ">= 1 net per 2"
Hmisc::label(tab2[["mic_nc"]]) <- "Net Coverage"
Hmisc::label(tab2[["mic_npt"]]) <- ">= 1 net per 2"

colnames(tab2) <- c("Net Cov",">= 1 net per 2","Net Cov",">= 1 net per 2")

kable(tab2, align = c("c"),
      digits = 3,
      booktabs = TRUE) %>%
    kable_styling("pandoc" ,
                  # c("striped","bordered"), 
                  full_width = F,
                  font_size = 7) %>%
    add_header_above(c(" ", "RDT+" = 2, "MIC+" = 2)) %>%
    add_header_above(c(" ", "Dependent Variable" = 4)) %>%
    group_rows("Time", 2, 4) %>%
    group_rows("Spatial", 5, 8) 
```


## Subsection title {#sec:2}

Referencing `r f.ref('tab_1')` is cool. as required. Don't forget to give each section
and subsection a unique label (see Sect. \ref{sec:results}).

#### Paragraph headings 

Use paragraph headings as needed.

\begin{align}
a^2+b^2=c^2
\end{align}






# References
